%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
% \lettersection{Position Application}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------


\begin{cvletter}
%---------------------------------------------------------------------
My name is Sergio Rosales, and I am writing to express my interest for
the position of \textit{GNC Engineer} at POLARIS. With my background
in design of robust systems, hands-on experience in R\&D, and
involvement in diverse software development projects, I am confident
that my skills are well suited for the position.

During my Master in Space Engineering project I focused on control
theory, orbital mechanics and trajectory optimization. My recent
involvement in the thermal engineering team at ArianeGroup further
deepened my understanding of aerospace design processes and reinforced
my ability to work in multidisciplinary teams. In addition to that,
during time in IMEMED, I led the electronics design team, working in
embedded systems development, which involved solving complex technical
challenges in real-world applications.

Additionally, as a member of the avionics team in the student
initiative ASTRA e.V., I contributed to the design of a rocket that
aims to reach the Kármán line. My experience there included the use of
sensor fusion for attitude determination. Similarly, at AGROINBO, I
automated an almond dehydration system with a PI PLC-controlled
closed-loop architecture. This required balancing thermal dynamics of
the system; a knowledge transferable to the optimization of GNC
subsystems. While my direct experience in flight controller coding is
minimal, my proficiency in Python and MATLAB/Simulink provides a
strong foundation for rapid upskilling in trajectory optimization
tools like STK or ROS.

I share POLARIS Raumflugzeuge GmbH's commitment to innovation,
efficiency, and technical excellence. This makes me eager to seize the
opportunity of growing my leadership skills, refining collaborative
problem-solving in multidisciplinary environments and expanding my
professional knowledge.

I'm ready to bring my experience in embedded systems and start as a
GNC engineer in the company bringing my technical and leadership
skills to the field. I appreciate your consideration and welcome the
opportunity to discuss the position.\hfill\break
I look forward to your reply.
%---------------------------------------------------------------------
\end{cvletter}