%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  %\cventry{<Degree>}{<Institution>}{<Location>}{<Date>}{<Description>}
  \cventry{M.Sc. in Space Engineering}
  {University of Bremen}
  {Bremen, Germany}
  {April 2022 - Current}
  {
    \begin{cvitems}
      \item \textbf{Master thesis:} Analysis of an Active Thermal
      Control System for the Avionics Equipment for Future
      Upper-Stages of a Launcher System.
      \begin{itemize}
        \item[\bullet] Python, ESATAN and ESARAD modeling. 
      \end{itemize}
      \item \textbf{Master project:} Research in techniques to
      mitigate errors of CNNs in radiation space environments.
      \begin{itemize}
        \item[\bullet] Python, C and C++ development benchmark
        development with Tensorflow. 
      \end{itemize}
      \item \textbf{Courses:} Trajectory Optimization, Spacecraft
      Navigation and Control, Communications Technologies for Space,
      Concurrent Engineering, FEM simulations for the design of space
      systems, Fluid Handling in spacecrafts, Structural design and
      analysis, Control theory, Orbital systems.
    \end{cvitems}
  }

  \cventry{Bachelor Degree in Mechatronics Engineering}
  {Catholic University of Bolivia ``San Pablo''}
  {Cochabamba, Bolivia}
  {February 2013 - February 2018}
  {
    \begin{cvitems}
      \item Graduated with Honor Distinction: Top of the 2018 class.
      \item \textbf{Main occupational skills covered:} Automation and
      control engineering, Signal processing, Fluid mechanics and
      thermodynamics, Vector mechanics.
      \item \textbf{Bachelor thesis:} Design and development of a
      prototype robot to explore and detect cracks in drinking water
      pipes using Convolutional Neural Networks.
    \end{cvitems}
  }

  \cventry{High School Diploma}
  {La Salle High School}
  {Cochabamba, Bolivia}
  {December 1999 - December 2012}
  {
    \begin{cvitems}
      \item{Passed with Distinctions.}
    \end{cvitems}
  }
  % \cvsubentry{What degree is this}
  %   {Diploma}
  %   {2001}
  %   {
  %     \begin{cvitems}
  %       \item {Passed with Distinctions.}
  %       \item {Specialised in Physics, Chemistry, and Maths with Computer Science}
  %     \end{cvitems}
  %   }
  %---------------------------------------------------------
\end{cventries}
