%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  %\cventry{<Job title>}{<Organization>}{<Location>}{<Date>}{<Description>}
  \cventry{Werkstudent}
  {ArianeGroup JTMU 5}
  {Bremen, Germany}
  {July 2023 - June 2024}
  {
    \begin{cvitems}
      \item Part time student job as support for thermal tasks in JTMU
      5.
      \item Support in multiple discipline tasks related to:
      \begin{itemize}
        \item[\checkmark] Develop fully automated migration of Version
        Control Systems from Bazaar to Git using Python.
        \item[\checkmark] Post processing of data for interfaces
        purposes in Python.
        \item[\checkmark] Automation of ESATAN script generation
        through Python and Matlab post-processing.
      \end{itemize}
      \item Support in simulations for both geometrical and thermal
      models tasks with ESATAN and ESARAD.
      \item \textbf{Technical Skills:} ESATAN, ESARAD, MATLAB, Python,
      Bazaar, Git, Bitbucket, Jira.
      \item \textbf{Soft Skills:} Adaptability, Communication,
      Decision-Making, Teamwork, Resource Management.
    \end{cvitems}
  }

  \cventry{Research and Development Engineer}
    {IMEMED}
    {Cochabamba, Bolivia}
    {April 2020 - March 2022}
    {
      \begin{cvitems}
        \item Full time job in collaborative research and development
        of medical equipment.
        \item Developed and manufactured the company's first medical
        equipments:
        \begin{itemize}
          \item[\checkmark] The first intensive care unit medical
          ventilator in Bolivia.
          \item[\checkmark] A X-Ray portable machine of 2DOF.
          \item[\checkmark] Prototype of a PSA oxygen concentrator
          plant of 180 \unit{m^{3}.h^{-1}}.
        \end{itemize}
        \item Collaborated with the software development team in
        back-end and front-end solutions for the 3 prototype
        equipments.
        \item Led the electronics design team and managed the design
        process of PCB prototypes for the ICU ventilator from the
        conceptualization up to manufacturing and testing in the span
        of 2 years.
        \item Carried out technical presentations to business
        partners, governmental institutions and medical facilities in
        3 regions of the country.
        \item Carried out negotiations with international technology
        partners, such as Masimo, B\"urkert and Demcon to reach OEM
        solutions for the company and product acquisition deals.
        \item \textbf{Technical Skills:} Altium Designer, Eagle
        Designer, C\#, Wpf, C++, Solidworks, MATLAB, Simulink,
        Microsoft Office, \LaTeX.
        \item \textbf{Soft Skills:} Leadership, Adaptability,
        Communication, Decision-Making, Teamwork, Resource Management,
        Negotiation skills, Presentation skills.
      \end{cvitems}
    }

  \cventry{University lecturer}
    {Catholic University of Bolivia ``San Pablo''}
    {Cochabamba, Bolivia}
    {July 2020 - December 2020}
    {
      \begin{cvitems}
        \item Teaching of the subject ``Physics Fundamentals'' for
        newly admitted students.
        \item \textbf{Soft Skills:} Creativity, Integrity, Empathy.
      \end{cvitems}
    }

  \cventry{Control and Automation Engineer}
    {AGROINBO TFD}
    {Cochabamba, Bolivia}
    {November 2018 - December 2019}
    {
      \begin{cvitems}
        \item Designed and implemented the complete system of
        automation for the process of dehydration of almonds which
        improved productivity of the company in 300\% and reduced time
        duration of production in 80\%.
        \item Designed the electric layout using CAD modeling tools
        and executed the implementation of the cable net connection.
        \item Characterized the system and designed a thermal
        mathematical model of the almond ovens through sensor
        measurements.
        \item Conceptualization and implementation of a closed loop
        control system using a LOGO PLC to fully automate the
        production lines.
        \item Designed the peripherals for the system automation and
        programmed the safety routines for the controller.
        \item \textbf{Technical Skills:} MATLAB, Simulink, Ladder
        programming, LOGO! Soft Comfort, AutoCAD Electrical.
        \item \textbf{Soft Skills:} Problem-solving, Constraint
        optimizations, Resourcefulness, Logical thinking.
      \end{cvitems}
    }
\end{cventries}
