%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Volunteering}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  %\cventry{<Organization>}{<Project>}{<Location>}{<Date>}{<Description>}
  \cventry{ASTRA e.V.}
  {Avionics Team Member}
  {Cochabamba, Bolivia}
  {November 2022 - January 2024}
  {%
    \begin{cvitems}
      \item Electronics designs prototyping, soldering and testing.
      \item Flight computer programming and testing the elements of
      the Kármán Project Rocket.
      \item GPS sensor integration into the main system.
      \item Support in ASTRA's technical and non-technical activities.
    \end{cvitems}
  }% Always leave one line for the line break or paragraph breaks

  \cventry{IILC Latinamerican Institute of Leadership Cristóforos}
  {Instructor Volunteer Team Member}
  {Cochabamba, Bolivia}
  {May 2018 - November 2019}
  {%
    \begin{cvitems}
      \item Volunteer during leadership and oratory courses.
      \item Instruction and planning of the activities in oratory
      courses.
    \end{cvitems}
  }

  \cventry{IEEE Student Branch of the Catholic University of Bolivia
  ``San Pablo'' - Cochabamba}
  {IEEE Student Branch Chair}
  {Cochabamba, Bolivia} 
  {January 2018 - January 2019} 
  {%
    \begin{cvitems}
      \item Founding member of the first IEEE Student Branch of the
      Catholic University of Bolivia ``San Pablo'' - Cochabamba.
      \item Management of the Student Branch recruitment and promotion
      of events.
      \item Scheduling and planning of technical and non-technical
      activities for the Student Branch.
      \item Interface between other branches of the region.
    \end{cvitems}
  }

  \cventry{TEDx UCB Cochabamba}
  {Logistics Team Member}
  {Cochabamba, Bolivia}
  {May 2017 - August 2018}
  {%
    \begin{cvitems}
      \item Member of the management team of the first TEDx event in
      Cochabamba.
      \item Management of logistics activities of assets needed in the
      main event.
    \end{cvitems}
  }

\end{cventries}
